---
title: "Lastal_AlignmentStat"
date: "`r Sys.Date()`"
output: pdf_document
params:
  RunNameVar:
    value: x
  GenomeNameVar:
    value: x
  ProbTableLoc:
    value: x
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy = TRUE)
```

```{r load_packages, include=FALSE}
library(ggplot2)
library(scales)
```

```{r options, include=FALSE}
args<-commandArgs(TRUE)
```


```{r import_variables, include=FALSE}
RunName <- params$RunNameVar
GenomeName <- params$GenomeNameVar
ProbTable <- read.csv(params$ProbTableLoc, header = TRUE, stringsAsFactors = FALSE)
```

```{r SummaryStatCalculations, echo=FALSE}
All <- sum(ProbTable$CountOfMatchesAndMismatches) + sum(ProbTable$CountInsertions) + sum(ProbTable$CountDeletions)
Insertions <- sum(ProbTable$CountInsertions)/All*100
Deletions <- sum(ProbTable$CountDeletions)/All*100
Mismatch <- sum(ProbTable$AasC, ProbTable$AasG, ProbTable$AasT, ProbTable$CasA, ProbTable$CasG, ProbTable$CasT, ProbTable$GasA, ProbTable$GasC, ProbTable$GasT, ProbTable$TasA, ProbTable$TasC, ProbTable$TasG)
MismatchP <- Mismatch/All*100
TotalAccuracy = 100 - (sum(ProbTable$CountInsertions)/All*100) - (sum(ProbTable$CountDeletions)/All*100) -  (Mismatch/All*100)
```

# Genome Alignment Summary

This report presents genome alignment stats for for **`r RunName`**. 

The reference used for the genome alignment is:

**`r GenomeName`**

Summary stats for this alignment are:

Number of sequences aligned to reference: `r comma_format()(nrow(ProbTable))`

The number of aligned bases, insertions, and deletions is: `r comma_format()(All)`

  * This sums the number of matched and mismatched bases, plus detected insertions and deletions


The number of insertions is: `r comma_format()(sum(ProbTable$CountInsertions))`

  * As percent: `r comma_format()(Insertions)`

The number of deletions is: `r comma_format()(sum(ProbTable$CountDeletions))`

  * As percent: `r comma_format()(Deletions)`

The number of mismatches is: `r comma_format()(Mismatch)`

  * As percent: `r MismatchP`


# Overall Accuracy rate

The overall accuracy is: `r TotalAccuracy`%

\newpage

#Match/Mismatch Profile
```{r Mismatch, echo=FALSE}
NumExpectA <- sum(ProbTable$Correct_A, ProbTable$AasC, ProbTable$AasG, ProbTable$AasT)
AasA <- (sum(ProbTable$Correct_A)/NumExpectA*100)
AasC <- (sum(ProbTable$AasC)/NumExpectA*100)
AasG <- (sum(ProbTable$AasG)/NumExpectA*100)
AasT <- (sum(ProbTable$AasT)/NumExpectA*100)

NumExpectC <- sum(ProbTable$CasA, ProbTable$Correct_C, ProbTable$CasG, ProbTable$CasT)
CasC <- (sum(ProbTable$Correct_C)/NumExpectC*100)
CasA <- (sum(ProbTable$CasA)/NumExpectC*100)
CasG <- (sum(ProbTable$CasG)/NumExpectC*100)
CasT <- (sum(ProbTable$CasT)/NumExpectC*100)

NumExpectG <- sum(ProbTable$GasA, ProbTable$GasC, ProbTable$Correct_G, ProbTable$GasT)
GasG <- (sum(ProbTable$Correct_G)/NumExpectG*100)
GasA <- (sum(ProbTable$GasA)/NumExpectG*100)
GasC <- (sum(ProbTable$GasC)/NumExpectG*100)
GasT <- (sum(ProbTable$GasT)/NumExpectG*100)

NumExpectT <- sum(ProbTable$TasA, ProbTable$TasC, ProbTable$TasG, ProbTable$Correct_T)
TasT <- (sum(ProbTable$Correct_T)/NumExpectT*100)
TasA <- (sum(ProbTable$TasA)/NumExpectT*100)
TasC <- (sum(ProbTable$TasC)/NumExpectT*100)
TasG <- (sum(ProbTable$TasG)/NumExpectT*100)
```

## **Table 1** - Match/Mismatch Matrix

| | Ref_A | Ref_C | Ref_G | Ref_T |
:---------------|:------------:|:--------------:|:-------------:|:------------:|
Read_A | `r comma_format()(sum(ProbTable$Correct_A))` | `r comma_format()(sum(ProbTable$CasA))` | `r comma_format()(sum(ProbTable$GasA))` | `r comma_format()(sum(ProbTable$TasA))` |
Read_C | `r comma_format()(sum(ProbTable$AasC))` | `r comma_format()(sum(ProbTable$Correct_C))` | `r comma_format()(sum(ProbTable$GasC))` | `r comma_format()(sum(ProbTable$TasC))` |
Read_G | `r comma_format()(sum(ProbTable$AasG))` | `r comma_format()(sum(ProbTable$CasG))` | `r comma_format()(sum(ProbTable$Correct_G))` | `r comma_format()(sum(ProbTable$TasG))` |
Read_T | `r comma_format()(sum(ProbTable$AasT))` | `r comma_format()(sum(ProbTable$CasT))` | `r comma_format()(sum(ProbTable$GasT))` | `r comma_format()(sum(ProbTable$Correct_T))` |


## **Table 2** - Match/Mismatch Percent Matrix

| | Ref_A | Ref_C | Ref_G | Ref_T |
:---------------|:------------:|:--------------:|:-------------:|:------------:|
Read_A | `r AasA` | `r CasA` | `r GasA` | `r TasA`
Read_C | `r AasC` | `r CasC` | `r GasC` | `r TasC`
Read_G | `r AasG` | `r CasG` | `r GasG` | `r TasG`
Read_T | `r AasT` | `r CasT` | `r GasT` | `r TasT`


## Transitions vs transversions

Probability a mismatch is a transition: `r (sum(AasG, GasA, CasT, TasC)/4)`

Probability a mismatch is a transversion: `r (sum(AasC, CasA, GasT, TasG, TasA, AasT, CasG, GasC)/8)`